CSCI 447: Project 1

### 2019-09-13 paper/paper.tex
Working on paper

\section{Problem Statement}

@@

% Loss functions
To assess the performance of our class prediction algorithm, we implemented two loss functions: Precision/Recall, and Cross Entropy.
% Loss function 1: Precision Recall
The Precision/Recall loss function computes two values, known as precision and recall, to measure the performance of our class prediction algorithm. This loss function utilizes the amounts of true positive, false positive, and false negative classifications for each class. Precision and recall are are computed as follows: 
$$Precision = \frac{1}{|C|} \sum^{|C|}_{i=1} \frac{TP_i}{TP_i + FP_i}$$
$$Recall = \frac{1}{|C|} \sum^{|C|}_{i=1} \frac{TP_i}{TP_i + FN_i}$$
$TP_i$ denotes the number of true positive classifications for class $i$, $FP_i$ denotes the number of false positive classifications for class $i$, and $FN_i$ denotes the number of false negative classifications for class $i$. $C$ is the set of all possible classes. Precision can be interpreted as a measure of how accurate true positive classifications, as it computes the fraction all positive classifications for a class that were truly positive. Recall measures accuracy among the values for each class that should have been positive, as it computes the fraction of all values that truly belonged to a class that were classified as positive.

@@

\acks{Acknowledgements go here.}

>>>>

\section{Problem Statement}
For this assignment, we were provided with 5 real world datasets. In each dataset, all data points were comprised of both quantitative and categorical variables, and each dataset had a designated classification. Our task was to train an algorithm to predict the classification of a given datapoint.  Our algorithm was trained by computing probabilities of each unique attribute value among the different classifications within each dataset, and then use to these probabilities to predict the classification of any datapoint. We then implemented two loss functions to measure the accuracy of our prediction algorithm.

@@

% Loss functions
To assess the performance of our class prediction algorithm, we implemented two loss functions: Precision/Recall, and 0/1 Loss.
% Loss function 1: Precision Recall
The Precision/Recall loss function computes two values, known as precision and recall, to measure the performance of our class prediction algorithm. This loss function utilizes the amounts of true positive, false positive, and false negative classifications for each class. Precision and recall are are computed as follows: 
$$Precision = \frac{1}{|C|} \sum^{|C|}_{i=1} \frac{TP_i}{TP_i + FP_i}$$
$$Recall = \frac{1}{|C|} \sum^{|C|}_{i=1} \frac{TP_i}{TP_i + FN_i}$$
$TP_i$ denotes the number of true positive classifications for class $i$, $FP_i$ denotes the number of false positive classifications for class $i$, and $FN_i$ denotes the number of false negative classifications for class $i$. $C$ is the set of all possible classes. Precision can be interpreted as a measure of how accurate true positive classifications, as it computes the fraction all positive classifications for a class that were truly positive. Recall measures accuracy among the values for each class that should have been positive, as it computes the fraction of all values that truly belonged to a class that were classified as positive[1].

@@

\acks{

Davis, Jesse, and Mark Goadrich. "The Relationship between Precision-Recall and ROC Curves." Proceedings of the 23rd International Conference on Machine Learning - ICML 06, 2006, doi:10.1145/1143844.1143874.

}
